A practical look at genetic algorithms

### 2015-11-20 evolutionaryComputation/practicals/report.tex
updated the todo list
having the initial expiriment setup, but I should do some more debugging tomorrow...

Trap functions were simply wrongly implemented, instead of counting the
ones they gave positional values of the ones in the block and used the
block as a lookup value for that.
\section{Execution}
%TODO:
% 1. Tournement selection is now implemented wrongly
%	* group(2) to select the first half off the parents
%	* randomly shuffle and group(2) again to select the second half
% 2. Mutation, should be trivial with help of the members factory, decide how
	% many bits will be mutated and then mutate those.
% 3. Offspring generation should create 2 instead of one.
% 4. Experiments
%	Create tables % including:
%		* min pop size for 29 out of 30 runs successful.
%		* The average number of generations
%		* The average CPU time required for running the GA with minimal pop size
%		* average should be over 30 runs
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y

>>>>

Trap functions were simply wrongly implemented, instead of counting the
ones they gave positional values of the ones in the block and used the
block as a lookup value for that.
\subsection{Uncertainties}
Should the elitism selection use tournement selection?
When precisly do we find the optimal solution?
	Should I wait for convergence or just say a string
	of all ones is good enough?
	Is 1 solution good enough or should all members have
	that solution
	I'm assuming 1 solution and that I can give a string
	of just ones.
How many generations to consider. I chose arbitrarly 10.

About randomly linked:
	There is another way to do it: for every member randomly link
	differently, and randomly pick 1 randomly linked instructionset
	for offspring generation (or do the strongest).
	Currently I do the global randomly linked, every run will however
	have the same randomly linked value, I'm aware of this.
\section{Execution}
%TODO:
% 1. Experiments
%	Create tables % including:
%		* min pop size for 29 out of 30 runs successful.
%		* The average number of generations
%		* The average CPU time required for running the GA with minimal pop size
%		* average should be over 30 runs
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
% maybe some more testing of the crossovers?
% also try to implement a threading scheme??
